Outline

### 2020-06-10 outline.Rmd
adding links to similar papers
updates to outline & refs

# Main Text
  - A key design principle was to create tools that can be integrated in existing analysis pipelines, in addition to allowing users to create new ones.
## Figure: flowchart of each step, getsequence-> run-> import -> visualize -> goto run
## Overarching design principles/{memer} framework
  - MEME utilities work with files on disk & outputs data to files on disk
  - {memer} works by handling writing files from R object inputs, constructing the commandline calls, then reading in the data from the output files.
      - by default, this is all done using temporary files, so the data is not permanently stored on disk.
      - This is to shift the perspective from needing to save the files, to focusing on writing reproducible code which can regenerate the data when run.
      - However, users can set the `outdir` argument to purposefully save the outputs to disk if needed.
        - Also, if users use a 'fasta' file as input, the output data will be stored alongside the fasta file location
  - For functions that use MEME commandline tools, they need the location of 'meme/bin/' on disk, we provide utilities for making this detection simple to reduce friction of using the tool.
    - `check_meme_install` does user-friendly check that meme can be detected from R environment
    - Environment variable `MEME_PATH` (set & forget), `options(meme_path)` (configure for each script), `meme_path` argument, for each function call
  - Whenever possible, {memer} uses standard R data types for better integration with common analysis tools, like `dplyr`, `GenomicRanges`, or base R. In this way, users don't need to learn new ways of working with data.

@@

@@

>>>>

# Results 
## Design & Implementation
  - A key design principle was to create tools that can be integrated in existing analysis pipelines, in addition to allowing users to create new ones.
## Figure: flowchart of each step, getsequence-> run-> import -> visualize -> goto run
## Overarching design principles/{memer} framework
  - MEME utilities work with files on disk & outputs data to files on disk
  - {memer} works by handling writing files from R object inputs, constructing the commandline calls, then reading in the data from the output files.
      - by default, this is all done using temporary files, so the data is not permanently stored on disk.
      - This is to shift the perspective from needing to save the files, to focusing on writing reproducible code which can regenerate the data when run.
      - However, users can set the `outdir` argument to purposefully save the outputs to disk if needed.
        - Also, if users use a 'fasta' file as input, the output data will be stored alongside the fasta file location
  - For functions that use MEME commandline tools, they need the location of 'meme/bin/' on disk, we provide utilities for making this detection simple to reduce friction of using the tool.
    - `check_meme_install` does user-friendly check that meme can be detected from R environment
    - Environment variable `MEME_PATH` (set & forget), `options(meme_path)` (configure for each script), `meme_path` argument, for each function call
  - Whenever possible, {memer} uses standard R data types for better integration with common analysis tools, like `dplyr`, `GenomicRanges`, or base R. In this way, users don't need to learn new ways of working with data, and outputs can be integrated with other tools with limited effort.

@@

## Availability & Future Directions
 - github (bioconductor?)
 - Support additional MEME Suite tools & visualizations

@@

# Other issues:
 - PWMEnrich (similar to AME) is now deprecated in bioconductor 3.12 (author request)
 - MotIV (has TOMTom like function) is now deprecated in 3.12

# Similar software papers:
https://journals.plos.org/ploscompbiol/article?id=10.1371/journal.pcbi.1007654

https://journals.plos.org/ploscompbiol/article?id=10.1371/journal.pcbi.1007664
